Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-17 ieee_paper.tex
sec 2 notations

\todo{describe the data structure} Since the sparsity of each row is
constant, ELLPACK becomes the most appropriate matrix
compression scheme.

\newfig{figures/matrix_structure.pdf}{\linewidth}{Matrix Structure.}{fig:mat_struct}

>>>>

In term of memory layout, we choose a format similar to the ELLPACK
format to store the matrix since the number of non zero per row is
constant throughout the matrix. The matrix is given in two arrays. The
first one is the classical {\tt col\_id} array that describes the
sparsity structure of the matrix. For each row it consists of $n_z$
consecutive entries which give in which column is the non zero. The
other array is the {\tt data} array which gives the values of the non
zero in the four matrices. The values of the matrices are interleaved
so that the value $A^l_{col\_id[k]}$ of the $k$th non zero of the
$l$th matrix is at index $(k-1)*4+l-1$. The vectors {\tt x} are also
similarly interleaved so that {\tt x}$^l_i$ and {\tt x}$^{l+1}_i$ are
consecutive in memory. The vector {\tt y} is similarly
interleaved. This is schematically shown in Figure~\ref{fig:mat_struct}.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/matrix_not.pdf}
  \caption{Matrix Structure.}
  \label{fig:mat_struct}
\end{figure}
